Output Summary

### 2020-10-20 03-post-process/output-plots.Rmd
Add rmd option to turn off drawing mcmc diagnostic plots

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: html_document
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
editor_options: 
  chunk_output_type: console
---

@@

## Diagnostic Plots {.tabset .tabset-pills}

### `alpha`, `beta`

```{r alpha-beta-diag-plots, fig.width = 4, fig.height = 5}
diag_plots(post, c("alpha", "beta"), layout = "2x1")
```

### `gamma`

```{r gamma-diag-plots, fig.width = 3, fig.height = 6}
diag_plots(post, "gamma", layout = "4x1")
```

### `^mu`

```{r mu-diag-plots, fig.width = 7, fig.height = 7}
diag_plots(post, "^mu", layout = "5x3")
```

### `^sig`

```{r sig-diag-plots, fig.width = 7, fig.height = 7}
diag_plots(post, "^sig", layout = "5x3")
```

### `init_recruits`

```{r init-recruits-diag-plots, fig.width = 5, fig.height = 7}
diag_plots(post, "init_recruits", layout = "4x2")
```

>>>>

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: html_document
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

`r if (params$mcmc_plots) "## Diagnostic Plots {.tabset .tabset-pills}"`

`r if (params$mcmc_plots) "### $\\alpha$, $\\beta$"`

```{r alpha-beta-diag-plots, eval = params$mcmc_plots, fig.width = 4, fig.height = 5}
diag_plots(post, c("alpha", "beta"), layout = "2x1")
```

`r if (params$mcmc_plots) "### $\\gamma$"`

```{r gamma-diag-plots, eval = params$mcmc_plots, fig.width = 3, fig.height = 6}
diag_plots(post, "gamma", layout = "4x1")
```

`r if (params$mcmc_plots) "### $\\mu$"`

```{r mu-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
diag_plots(post, "^mu", layout = "5x3")
```

`r if (params$mcmc_plots) "### $$\\sigma$"`

```{r sig-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
diag_plots(post, "^sig", layout = "5x3")
```

`r if (params$mcmc_plots) "### init_recruits"`

```{r init-recruits-diag-plots, eval = params$mcmc_plots, fig.width = 5, fig.height = 7}
diag_plots(post, "init_recruits", layout = "4x2")
```
